Cache is King: Presenting a Suite of Fast, Correlation Function Codes

### 2015-01-22 paper/ms.tex
Removed sglib header from countpairs_rp_pi

\section{Benchmarks \& Scaling}
In this section we present the runtimes and OpenMP scaling for the different codes.

>>>>

\section{Benchmarks \& Scaling}
In this section we present the runtimes and OpenMP scaling for the three codes.

\subsection{Scaling with OpenMP threads}
\begin{figure}[htbp]
\includegraphics[clip=true,width=0.5\linewidth]{xi_of_r_scaling_Mr19}%
\includegraphics[clip=true,width=0.5\linewidth]{xi_rp_pi_scaling_Mr19}\\
\includegraphics[clip=true,width=0.5\linewidth]{wp_scaling_Mr19}%
\caption{OpenMP scaling for the \xir, \xirppi, \wprp }
\end{figure}
